Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
moving note about facilitators to intro

@@

In WSSSPE3, we attempted to take what we learned from WSSSPE1 and WSSSPE2 in how
we can collaboratively build a workshop agenda and turn that into an ongoing
community activity. For the first time in WSSSPE meetings, two professional
event organizers and facilitators were engaged using funding available to the
WSSSPE3 organizing committee. They assisted the organizing committee members
planning the workshop agenda during the months leading up to the conference.
Throughout the workshop, they actively engaged participants with variously
tools, activities, and reminders. The success or failure of these efforts will
only become apparent over time.

>>>>

WSSSPE3 also included two professional
event organizers/facilitators from Knowinnovation who helped the organizing committee members
plan the workshop agenda, and during the workshop, they actively engaged
participants with variously
tools, activities, and reminders.

@@

In WSSSPE3, we attempted to take what we learned from WSSSPE1 and WSSSPE2 in how
we can collaboratively build a workshop agenda and turn that into an ongoing
community activity. The success or failure of these efforts will
only become apparent over time.
